Pesticides in small agricultural streams in Germany

### 2016-08-26 article.tex
first draft

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[Pesticides small streams]{Pesticides in small agricultural streams in Germany}
\abbreviations{mo, pest, ger, tu}
\keywords{Monitoring, Neonicotinoid, Germany, Toxic Units, Freshwater}
% RAC,

@@

Our result suggest that pesticides might be a major thread for aquatic life.
However, future monitoring programs need to be unified between states to provide more reliable assessments.

\todo{not finished yet}

%% Word
\end{abstract}

@@

% Approval / Risk Assessment
Monitoring data, despite the outlined limitations, provides an opportunity to study environmental occurrences of pesticides after approval.
The high exceedances of RAC indicate that the approval process must be checked and refined.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[Pesticides small streams]{Pesticides in small agricultural streams in Germany}
% \abbreviations{mo, neon, ra, tu, fw}
\keywords{Monitoring, Neonicotinoid, Risk Assessment Toxic Units, Freshwater}
% RAC,

@@

Our result suggest that pesticides originating from agricultural land use might be a major thread for aquatic ecosystems.
The exceedances of RACs indicate risks originating from few compounds.
However, future monitoring programs need to be unified between states to provide more reliable assessments. \todo{Letzter Absatz gefällt mir nicht....}

%182 words
\end{abstract}

@@

% Approval / Risk Assessment
Monitoring data, despite the outlined limitations, provides an opportunity to study environmental occurrences of pesticides after approval.
The high exceedances of RAC indicate that the approval process for pesticides must be checked and refined.
